Competing Bandits: \\ The Perils of Exploration under Competition

### 2020-06-28 journal paper/content/sec-intro.tex
updates

Learning from interactions with consumers is ubiquitous in modern customer-facing systems, from product recommendations to web search to content selection to fine-tuning user interfaces. These interactions are essential for the development of high quality products, but, in order to learn what products are high quality, firms need to implement systems that engage in \emph{exploration}: deploying potentially suboptimal products in order to acquire new information to make more informed product decisions tomorrow.

In this paper, we initiate a study of the interplay between \exploration and \competition. Competition induces firms to want to produce high quality goods, but they need to learn how to do so via exploration. However, while exploration may provide firms with the necessary information to allow them to produce high quality products in the long-run, it may lead to bad experiences for consumers today and adversely affect a firm's reputation. This may incentivize subsequent consumers to go to the firm's competitors tomorrow and leave the firm with a lower market share and less consumers to learn from. Consumers therefore serve three distinct roles: they are customers that generate revenue, they are sources of data for learning, and they are self-interested agents who choose among the competing firms.

The main high-level question that we focus on in this paper is: {\bf does competition lead to the adoption of better exploration algorithms?} This translates into a number of more concrete questions. While it is commonly assumed that ``better" technology always helps, is this so for our setting? Does increasing competition lead to higher consumer welfare? To what extent is there a ``data feedback loop" where one firm having more data leads to that firm attracting more users which leads to that firm having more data, etc.?

@@

\xhdr{Main Findings.}
We find that in a simultaneous entry duopoly a greedy (myopic) algorithm that does no purposeful exploration is incentivized in equilibrium. In the expectation choice variant, once a firm does any exploration it is immediately starved of consumers when its opponent plays a greedy algorithm since we show that the expected reward for every subsequent consumer is higher for the firm that plays the greedy algorithm. In the reputation choice variant, the same mechanism drives the greedy algorithm to be incentivized in equilibrium. In this variant, exploration hurts a firm's reputation and decrease its market share in the near term. This leaves the firm with less users to learn from, which further degrades the firm's performance relative to competitors who keep learning and improving from \emph{their} customers, and so forth. Taken to the extreme, such dynamics lead to a ``death spiral" effect when the vast majority of customers eventually switch to competitors. As a result, our model provides an example of the mechanisms that can lead to a ``data feedback loop" that has been hypothesized in policy discussions. In both cases, consumer welfare is low since the greedy algorithm is known to be dramatically bad in many important cases of multi-armed bandits.

The primary mechanism that generates this stark result is that consumers need to be incentivized to select a firm over its competitors, leading firms that engage in exploration to be starved of consumers before they make enough progress on their learning problem. In order to incentivize ``better" exploration strategies the key intuition is that the firm needs to have some ``free" consumers that visit them without the firm having to incentivize them to do so. This allows the firm to eventually overcome the initial losses in consumer perception from exploration.

We relax the decision rule of the consumers to allow for each firm to be chosen with some fixed baseline probability so that firms get a constant stream of ``free" consumers; we call this choice rule \HardMaxRandom. We find that, in this setting, better algorithms help in a big way: a sufficiently better algorithm is guaranteed to win all non-random agents after an initial learning phase. While the precise notion of ``sufficiently better algorithm" is rather subtle, we note that commonly known ``smart" bandit algorithms typically defeat the commonly known ``naive" ones, and the latter typically defeat the greedy algorithm. However, there is a substantial caveat: one can defeat any algorithm by interleaving it with the greedy algorithm. This has two undesirable corollaries: a better algorithm may sometimes lose, and a pure Nash equilibrium typically does not exist.

We use the reputation choice variant to analyze the effect of varying the timing of entry between the firms and allow one firm to have a first-mover advantage so that this firm (denoted as the incumbent) gets all the agents in the market before the other firm enters. We find that, if the first-mover period is sufficiently large, then the incumbent has a dominant strategy to play ``smart" bandit algorithms and that consumer welfare is substantially higher than in the case of simultaneous entry. The intuition is simply that a sufficiently long incumbency period allows the firm to make sufficient progress on its learning problem that it can overcome the original drop in its reputation from exploration in the beginning rounds.

@@

\xhdr{Noise in consumer choice}: We further relax the decision rule of the agents so that the probability of choosing a given principal varies smoothly as a function of the difference between  principals' expected rewards; we call it \SoftMaxRandom. For this decision rule, the ``better algorithm wins" result holds under much weaker assumptions on what constitutes a better algorithm. This is the most technical result of the paper. The competition in this setting is necessarily much more relaxed: typically, both principals attract approximately half of the agents as time goes by (but a better algorithm may attract slightly more).

We use the reputation choice variant to explore numerically the extent to which better algorithms under the \HardMaxRandom decision rule are incentivized in realistic time-scales. We show that for small but still ``relevant" parameter values, this effect does not show up for unless the time horizon is very long. \\
\xhdr{Reputation and Data First-Mover Advantage}
In the reputation choice variant, we investigate the ``first-mover advantage" phenomenon in more detail. Being first in the market gives free data to learn from (a ``data advantage") as well as a more definite, and possibly better reputation compared to an entrant (a ``reputation advantage"). We run additional experiments so as to isolate and compare these two effects. We find that either effect alone leads to a significant advantage under competition. The data advantage is larger than reputation advantage when the incumbent commits to a more advanced bandit algorithm.

Data advantage is significant from an anti-trust perspective, as a possible barrier to entry. We find that even a small amount ``data advantage" gets amplified under competition, causing a large difference in eventual market shares. This observation runs contrary to prior work  \cite{lambrecht2015can,bajari2018impact}, which studied learning without competition, and found that small amounts of additional data do not provide significant improvement in eventual outcomes. We conclude that competition dynamics -- that firms compete as they learn over time -- are pertinent to these anti-trust considerations.

@@

\caption{Inverted-U relationship between competitiveness and algorithms.}
\label{fig:inverted-U}
\end{center}
\end{figure}
\xhdr{Economic interpretation.}
The inverted-U relationship between the severity of competition among firms and the quality of technologies that they adopt is a familiar theme in the economics literature \citep[\eg][]{Aghion-QJE05,Vives-08}.%
\footnote{The literature frames this relationship as one between ``competition" and ``innovation". In this context, ``innovation" refers to adoption of a better technology, at a substantial R\&D expense to a given firm. It is not salient whether similar ideas and/or technologies already exist outside the firm. It is worth noting that the adoption of exploration algorithms tends to require substantial R\&D effort in practice, even if the algorithms themselves are well-known in the research literature; see \citet{MWT-WhitePaper-2016} for an example of such R\&D effort.}
We find it illuminating to frame our contributions in a similar manner, as illustrated in \reffig{fig:inverted-U}.

In our model, competition varies based on the number of ``free" consumers that a firm receives. One economic mechanism that can generate this comes from introducing ``random" consumers where we vary from fully rational decisions with \HardMax to relaxed rationality with \HardMaxRandom to an even more relaxed rationality with \SoftMaxRandom. Indeed, with \HardMax you lose all customers as soon as you fall behind in performance, with \HardMaxRandom you get some small market share no matter what, and with \SoftMaxRandom you are further guaranteed a market share close to $\tfrac12$ as long as your performance is not much worse than the competition. The uniform choice among principals corresponds to no rationality and no competition. Another economic mechanism that can generate this comes from the number of firms and the timing of entry in the market. Competition in this case ranges from monopoly to ``incumbent" (first-mover in duopoly) to simultaneous entry duopoly to ``late entrant" (last mover in duopoly). The same distinctions in both cases also control the severity of competition between the principals.

In both variants we identify an inverted-U relationship between competition and innovation in the spirit of \reffig{fig:inverted-U}. These inverted-U relationships arise for a fundamentally different reason, compared to the existing literature on ``competition vs. innovation.'' In the literature, better technology always helps in a competitive environment, other things being equal. Thus, the trade-off is between the costs of improving the technology and the benefits that the improved technology provides in the competition. Meanwhile, we find that a better exploration algorithm may sometimes perform much worse under competition, even in the absence of R\&D costs. This stems from the nature of exploration technologies in online markets which rely on learning from interactions with users. This leads to an implicit cost from exploration in the form of a reduced rate of users that a firm attracts and can learn from. However, interestingly, the economic mechanism in our model for incentivizing firms to engage in R\&D has a qualitative similarity to the role that patents play in incentivizing innovation in standard R\&D models. In these models, patents temporarily relax competition for the innovating firm by giving them exclusive access to their innovation for a limited period of time in order to incentivize them to invest in the better technology. In our model, temporarily relaxing competition in the form of giving firms free periods to learn incentivizes the firm to invest in the better technology.

@@

\xhdr{Map of the paper.}
We survey related work (Section~\ref{sec:related-work}), lay out the model and preliminaries (Section~\ref{sec:model}), and proceed to analyze the different models. We start by analyzing the expectation choice model analytically. In Sections ~\ref{sec:rational},~\ref{sec:random}, and ~\ref{sec:soft} we analyze the expectation choice variant and characterize the equilibrium behavior under three different agent decision rules. Then, we turn to analyze the reputation choice variant of the model with details of the analysis described in Section ~\ref{sec:sim_details}. Sections ~\ref{sec:isolation} and ~\ref{sec:revisited} overview results from running different bandit algorithms in isolation (i.e. without competition). Sections ~\ref{sec:competition} and ~\ref{sec:barriers} overview the results of the reputation choice variant. Section ~\ref{sec:non_greedy} presents results of varying the consumer choice rule in the reputation choice variant. Section ~\ref{sec:conclusion} concludes.

>>>>

Learning from interactions with users is ubiquitous in modern customer-facing systems, from product recommendations to web search to content selection to fine-tuning user interfaces. These interactions are essential for the development of high quality products, but, in order to learn what products are high quality, firms need to implement systems that engage in \emph{exploration}: deploying potentially suboptimal products in order to acquire new information to make more informed product decisions tomorrow.

In this paper, we initiate a study of the interplay between \exploration and \competition. The fundamental tension is that while exploration allows for the deployment of high quality products in the long-run, it leads to poor user experiences in the short-run. Exploration can therefore harm the perception users have of a system, which may lead them to instead utilize a competing system. This would leave the system with lower market share and therefore less users to learn from relative to its competitors and allow its competitors to make further progress on their learning problem. Users therefore serve three distinct roles: they are customers that generate revenue, they are sources of data for learning, and they are self-interested agents who choose among the competing systems.

The main high-level question that we focus on in this paper is whether competition between systems incentives the adoption of better exploration algorithms. This translates into a number of more concrete questions. While it is commonly assumed that ``better" technology always helps, is this so for our setting? Does increasing competition lead to higher consumer welfare? To what extent is there a ``data feedback loop" where one firm having more data leads to that firm attracting more users which leads to that firm having more data, etc.?\footnote{This is a fundamental question which is part of a larger policy discussion around whether data can serve as an indirect network effect and lead to similar ``market tipping" results as is standard in the literature on competition in markets with network effects (see \cite{jullien2019economics} for a policy oriented discussion of this).}

@@

\xhdr{Main Findings.}
We find that competition induces firms to commit to a greedy (myopic) algorithm in equilibrium that does no purposeful exploration. This leads to low consumer welfare since the greedy algorithm is known to be dramatically bad in many important cases of multi-armed bandits. The primary mechanism that generates this stark result is that consumers need to be incentivized to select a firm over its competitors, leading a firm that engages in exploration to be starved of consumers before it makes enough progress on its learning problem. In order to incentivize ``better" exploration strategies in equilibrium, the key intuition is that the firm needs to have some ``free" consumers that visit them without the firm having to incentivize them to do so. This allows the firm to eventually overcome the initial losses in consumer perception from exploration. We explore two economic mechanisms that can generate such an effect.

The first is the presence of users who randomly choose between the firms which gives each firm a constant stream of ``free" users and thus ensures it never gets fully starved. We find that, even when there is a small fraction of such consumers, better algorithms help in a big way: a sufficiently better algorithm is guaranteed to win all non-random agents after an initial learning phase.\footnote{While the precise notion of ``sufficiently better algorithm" is rather subtle, we note that commonly known ``smart" bandit algorithms typically defeat the commonly known ``naive" ones, and the latter typically defeat the greedy algorithm. However, there is a substantial caveat: one can defeat any algorithm by interleaving it with the greedy algorithm. This has two undesirable corollaries: a better algorithm may sometimes lose, and a pure Nash equilibrium typically does not exist.} However, while this holds asymptotically, our numerical experiments show that this requires either unreasonably large time scales or a large fraction of such users.

The second is that if one firm has a first-mover advantage then this firm gets free users before the other firm enters into the market. We show that if this incumbency period is sufficiently long, then it allows the firm to make sufficient progress on its learning problem and incentivizes it to commit to better algorithms. While this leads to the incumbent getting almost all of the market, it leads to higher consumer welfare than under competition when the firms enter at the same time.

@@

\xhdr{Reputation and Data Advantage}: In the reputation choice variant we investigate the first-mover advantage phenomenon in more detail. Being first in the market gives the incumbent free data to learn from (a ``data advantage") as well as a more definite, and possibly better reputation compared to an entrant (a ``reputation advantage"). We run additional experiments so as to isolate and compare these two effects. We find that either effect alone leads to a significant advantage under competition. The data advantage is larger than reputation advantage when the incumbent commits to a more advanced bandit algorithm. This result shows that even a small amount ``data advantage" gets amplified under competition, causing a large difference in eventual market shares.

\xhdr{Noise in consumer choice}: We further relax the decision rule of the agents so that the probability of choosing a given firm varies smoothly as a function of the difference between  principals' expected rewards. For this decision rule, the ``better algorithm wins" result holds under much weaker assumptions on what constitutes a better algorithm. This is the most technical result of the paper. The competition in this setting is necessarily much more relaxed: typically, both principals attract approximately half of the agents as time goes by (but a better algorithm may attract slightly more).

@@

\caption{Inverted-U relationship between competitiveness and algorithms.}
\label{fig:inverted-U}
\end{center}
\end{figure}
\xhdr{Economic interpretation.} Our model speaks to two distinct strands of the economics literature.

The first is the literature that studies the relationship between competition and innovation where, in our context,  the choice between different algorithms is interpreted as firms determining whether to invest in a ``better" technology as the degree of competition varies.\footnote{The choice of algorithms has a clear analogue to ``innovation" in our context as the literature on multi-armed bandits has identified distinct ``classes" of algorithms according to asymptotic regret bounds. Thus, choosing algorithms in ``better" classes corresponds with innovation on the part of the firm in our interpretation of the model. It is not salient whether similar ideas and/or technologies already exist outside the firm. It is worth noting that the adoption of exploration algorithms tends to require substantial R\&D effort in practice, even if the algorithms themselves are well-known in the research literature; see \citet{MWT-WhitePaper-2016} for an example of such R\&D effort.} A classic result in this literature is that there is an inverted-U relationship between the severity of competition among firms and the quality of technologies that they adopt is a familiar theme in the economics literature \citep[\eg][]{Aghion-QJE05,Vives-08}.

We find it illuminating to frame our contributions in a similar manner, as illustrated in \reffig{fig:inverted-U}. In our model we consider varying the intensity of competition as varying the degree to which a firm needs to incentivize users to visit them. Competition is less intense when there are more ``random" users or one firm has a sufficiently long first-mover advantage. The inverted-U relationship in our model arise for a fundamentally different reason, compared to the existing literature on ``competition vs. innovation.'' In the literature, better technology always helps in a competitive environment, other things being equal. Thus, the trade-off is between the costs of improving the technology and the benefits that the improved technology provides in the competition. Meanwhile, we find that a better exploration algorithm may sometimes perform much worse under competition, even in the absence of R\&D costs. This stems from the nature of exploration technologies in online markets which rely on learning from interactions with users. This leads to an implicit cost from exploration in the form of a reduced rate of users that a firm attracts and can learn from.

Interestingly, the economic mechanism in our model for incentivizing firms to engage in R\&D has a qualitative similarity to the role that patents play in incentivizing innovation in standard R\&D models. In these models, patents temporarily relax competition for the innovating firm by giving them exclusive access to their innovation for a limited period of time in order to incentivize them to invest in the better technology. In our model, temporarily relaxing competition in the form of giving firms free periods to learn incentivizes the firm to invest in the better technology.

The second is the nascent literature which studies the economics of data and how data can serve as a barrier to entry in the digital economy \cite{de2020data, hagiu2020data}. Our model directly speaks to this literature as we endogenize data-driven network effects by explicitly considering a model where firms are simultaneously solving a machine learning problem while competing against each other for users. The results of our model point to the fact that competition dynamics -- that firms compete as they learn over time and that this competition endogenously determines the data observed by firms -- are pertinent to understanding whether or not data can serve as a barrier to entry. Indeed, our results are similar to the market tipping results in the literature on indirect network effects and show a channel through which differences in data ownership can result in market tipping. However, it is important to note that the channel through which this arises in our model is not simply from differences in the quantity of data possessed by the firms, but also from the quality of the data.

@@

\xhdr{Map of the paper.}
We survey related work (Section~\ref{sec:related-work}), lay out the model and preliminaries (Section~\ref{sec:model}). We start by analyzing the expectation choice model analytically. In Sections ~\ref{sec:rational},~\ref{sec:random}, and ~\ref{sec:soft} we analyze the expectation choice variant and characterize the equilibrium behavior under three different agent decision rules. Then, we turn to analyze the reputation choice variant of the model with details of the analysis described in Section ~\ref{sec:sim_details}. Sections ~\ref{sec:isolation} and ~\ref{sec:revisited} overview results from running different bandit algorithms in isolation (i.e. without competition). Sections ~\ref{sec:competition} and ~\ref{sec:barriers} overview the results of the reputation choice variant. Section ~\ref{sec:non_greedy} presents results of varying the consumer choice rule in the reputation choice variant. Section ~\ref{sec:conclusion} concludes.

### 2020-06-28 journal paper/itcs18paper/sec-random.tex
the latex compiles
updates

Given an algorithm \alg[1] that deviates from \DynGreedy starting from
step $n_0$ and a ``mixing'' parameter $p$, we will construct a
modified algorithm as follows.
\begin{enumerate}
\item The modified algorithm coincides with \alg[1] (and \DynGreedy)
for the first $n_0-1$ steps;
\item In each step $n\geq n_0$, \alg[1] is invoked with probability
  $1-p$, and with the remaining probability $p$ does the ``greedy
  choice": chooses an action with the largest posterior mean reward
  given the current information collected by \alg[1].
\end{enumerate}
%The modified algorithm is called \emph{greedy deviation}, with probability parameter $p$.
For a cleaner comparison between the two algorithms, the modified algorithm does not record rewards received in steps with the ``greedy choice". Parameter $p>0$ is the same for all steps.

@@

\begin{proof}[Proof of Theorem~\ref{thm:random-greedy}]
  Let $\rew'_1(n)$ denote the Bayesian-expected reward of the ``greedy
  choice'' after after $n-1$ steps of \alg[1]. Note that
  $\rew_1(\cdot)$ and $\rew'_1(\cdot)$ are non-decreasing: the former
  because \alg[1] is monotone and the latter because the ``greedy
  choice'' is only improved with an increasing set of
  observations. Therefore, the modified algorithm \alg[2] is monotone
  by \eqref{eq:random-BIR}.

  By definition of the ``greedy choice,'' $\rew_1(n)\leq \rew'_1(n)$
  for all steps $n$. Moreover, by Lemma~\ref{lm:DG-rew},
  \alg[1] has a strictly smaller $\rew(n_0)$ compared to \DynGreedy;
  so, $\rew_1(n_0)<\rew_2(n_0)$.\sw{fixed inequalities; but this paragraph is still not perfectly clear}

Let $\alg$ denote a copy of \alg[1] that is running ``inside" the modified algorithm \alg[2]. Let $m_2(t)$ be the number of global rounds before $t$ in which the agent chooses principal $2$ \emph{and} \alg is invoked; in other words, it is the number of agents seen by \alg before global round $t$. Let $\mM_{2,t}$ be the agents' posterior distribution for $m_2(t)$.

We claim that in each global round $t\geq n_0$, distribution $\mM_{2,t}$ stochastically dominates distribution $\posteriorN{1}{t}$, and $\PMR_1(t)<\PMR_2(t)$. We use induction on $t$. The base case $t=n_0$ holds because $\mM_{2,t} = \posteriorN{1}{t}$ (because the two algorithms coincide on the first $n_0-1$ steps), and $\PMR_1(n_0)<\PMR_2(n_0)$ is proved as in \eqref{eq:pf:thm:DG-dominance}, using the fact that $\rew_1(n_0)<\rew_2(n_0)$.

The induction step is proved as follows. The induction hypothesis for global round $t-1$ implies that agent $t-1$ is seen by \alg with probability $(1-\eps_0)(1-p)$, which is strictly larger than $\eps_0$, the probability with which this agent is seen by \alg[2]. Therefore, $\mM_{2,t}$ stochastically dominates $\posteriorN{1}{t}$.
\begin{align}
\PMR_1(t)
  &= \Ex{n\sim \posteriorN{1}{t}} {\rew_1(n+1)} \nonumber \\
  &\leq \Ex{m\sim \mM_{2,t}} {\rew_1(m+1)}
    \label{eq:pf:thm:random-greedy-1}\\
  &< \Ex{m\sim \mM_{2,t}} {(1-p)\cdot \rew_1(m+1) + p\cdot \rew'_1(m+1)}
    \label{eq:pf:thm:random-greedy-2} \\
  &= \PMR_2(t). \nonumber
\end{align}
Here inequality \eqref{eq:pf:thm:random-greedy-1} holds because $\rew_1(\cdot)$ is monotone and $\mM_{2,t}$ stochastically dominates $\posteriorN{1}{t}$, and inequality \eqref{eq:pf:thm:random-greedy-2} holds because $\rew_1(n_0)<\rew_2(n_0)$ and $\mM_{2,t}(n_0)>0$.%
\footnote{If $\rew_1(\cdot)$ is strictly increasing, then inequality \eqref{eq:pf:thm:random-greedy-1} is strict, too; this is because $\mM_{2,t}(t-1)>\posteriorN{1}{t}(t-1)$.  }
\end{proof}

>>>>

Given an algorithm \alg[1] that deviates from \DynGreedy starting from
step $n_0$ and a ``mixing'' parameter $p$, we will construct a
modified algorithm as follows.
\begin{enumerate}
\item The modified algorithm coincides with \alg[1] (and \DynGreedy)
for the first $n_0-1$ steps;
\item In each step $n\geq n_0$, \alg[1] is invoked with probability
  $1-p$, and with the remaining probability $p$ does the ``greedy
  choice": chooses an action with the largest posterior mean reward
  given the current information collected by \alg[1].
\end{enumerate}
%The modified algorithm is called \emph{greedy deviation}, with probability parameter $p$.
For a cleaner comparison between the two algorithms, the modified algorithm does not record rewards received in steps with the ``greedy choice". Parameter $p>0$ is the same for all steps. We state the main result and defer the detailed proof to the appendix.

@@

### 2020-06-28 journal paper/itcs18paper/sec-rational.tex
updates

A more challenging scenario is when the tie-breaking is biased in favor of principal 1, but not deterministically so: $\respF(0)>\tfrac12$. Then this principal also has a ``winning strategy" no matter what the other principal does. Specifically, principal 1 can get all but the first few agents, under a mild technical assumption that \DynGreedy deviates from \StaticGreedy. Principal 1 can use \DynGreedy, or any other monotone MAB algorithm that coincides with \DynGreedy in the first few steps.

@@

\begin{proof}
The proof re-uses Lemmas~\ref{lm:DG-rew} and~\ref{lm:DG-sudden}, which do not rely on fair tie-breaking.

Because of the biased tie-breaking, for each global round $t$ we have:
\begin{align}\label{eq:thm:HardMax-biased-PMRtoPr}
\text{if $\PMR_1(t)\geq \PMR_2(t)$ then $\Pr[i_t=1]>\tfrac12$.}
\end{align}
Recall that $i_t$ is the principal chosen in global round $t$.

Let $m_0$ be the first step when \alg[2] deviates from \DynGreedy, or \DynGreedy deviates from \StaticGreedy, whichever comes sooner. \asedit{Then \alg[2], \DynGreedy and \StaticGreedy coincide on the first $m_0-1$ steps. Moreover, $m_0\leq n_0$ (since \DynGreedy deviates from \StaticGreedy at step $n_0$), so \alg[1] coincides with \DynGreedy on the first $m_0$ steps.

So, $\rew_1(n)=\rew_2(n)$ for each step $n<m_0$, because \alg[1] and \alg[2] coincide on the first $m_0-1$ steps. Moreover, if \alg[2] deviates from \DynGreedy at step $m_0$ then
    $\rew_1(m_0) > \rew_2(m_0)$ 
by Lemma~\ref{lm:DG-rew}; else, we trivially have
    $\rew_1(m_0) = \rew_2(m_0)$.} To summarize:
\begin{align}\label{eq:thm:HardMax-biased-rew}
    \rew_1(n)\geq\rew_2(n)\quad \text{for all steps $n\leq m_0$}.
\end{align}

We claim that $\Pr[i_t=1]>\tfrac12$ for all global rounds $t\leq m_0$. We prove this claim using induction on $t$. The base case $t=1$ holds by \eqref{eq:thm:HardMax-biased-PMRtoPr} and the fact that in step 1, \DynGreedy chooses the arm with the highest prior mean reward. For the induction step, we assume that $\Pr[i_t=1]>\tfrac12$ for all global rounds $t<t_0$, for some $t_0\leq  m_0$. It follows that distribution $\posteriorN{1}{t_0}$ stochastically dominates distribution $\posteriorN{2}{t_0}$.%
\footnote{For random variables $X,Y$ on \R, we say that $X$ \emph{stochastically dominates} $Y$ if $\Pr[X\geq x] \geq \Pr[Y\geq x]$ for any $x\in \R$.}
Observe that
\begin{align}\label{eq:thm:HardMax-biased-PMR-aux}
\PMR_1(t_0)
  = \Ex{n\sim \posteriorN{1}{t_0}} {\rew_1(n+1)}
  \geq \Ex{n\sim \posteriorN{2}{t_0}} {\rew_2(n+1)}
  = \PMR_2(t_0).
\end{align}
So the induction step follows by \eqref{eq:thm:HardMax-biased-PMRtoPr}. Claim proved.

Now let us focus on global round $m_0$, and denote $\mN_i = \posteriorN{i}{m_0}$.  By the above claim,
\begin{align}\label{eq:thm:HardMax-biased-mN}
\text{$\mN_1$ stochastically dominates $\mN_2$, and moreover
    $\mN_i(m_0-1)>\mN_i(m_0-1)$.}
\end{align}

By definition of $m_0$, either (i) \alg[2] deviates from \DynGreedy starting from local step $m_0$, which implies $\rew_1(m_0)> \rew_2(m_0)$ by Lemma~\ref{lm:DG-rew}, or (ii) \DynGreedy deviates from \StaticGreedy starting from local step $m_0$, which implies $\rew_1(m_0)>\rew_1(m_0-1)$ by Lemma~\ref{dgmono}. In both cases, using \eqref{eq:thm:HardMax-biased-rew} and \eqref{eq:thm:HardMax-biased-mN}, it follows that the inequality in \eqref{eq:thm:HardMax-biased-PMR-aux} is strict for $t_0=m_0$.

Therefore, agent $m_0$ chooses principal $1$, and by Lemma~\ref{lm:DG-sudden} so do all subsequent agents.
\end{proof}

>>>>

A more challenging scenario is when the tie-breaking is biased in favor of principal 1, but not deterministically so: $\respF(0)>\tfrac12$. Then this principal also has a ``winning strategy" no matter what the other principal does. Specifically, principal 1 can get all but the first few agents, under a mild technical assumption that \DynGreedy deviates from \StaticGreedy. Principal 1 can use \DynGreedy, or any other monotone MAB algorithm that coincides with \DynGreedy in the first few steps. We state the result and defer the proof to the appendix.

@@
